The following chapter contains short introductions to the most important technologies used in the project. 

\section*{Glasgow Haskell Compiler} %-- Haskell afsnit istedet??
Out of the currently available Haskell compilers we use the Glasgow Haskell Compiler (GHC) on the backend for interpreting the Haskell exercises and running the test suite. GHC was chosen over the other compilers due to it being the standard compiler recommended by the Haskell Organization \cite{Haskell_GHC} and it being the compiler used in the Haskell Course.

\section*{Hspec}
To enable running Haskell tests on the backend we needed a test framework. Here a test framework allows us to define the tests that need to be automatically run on the coding exercises the students submit. This allows us to confirm if the students completed the exercise and if not provide them with feedback on what tests their code failed.
Hspec was chosen instead of other test frameworks since it allows the professor to define the tests in an easy-to-understand domain-specific language (DSL). 
This makes the framework easier to work with as a DSL is a language targeted towards a specific domain it allows Hspec to tests to be easily written and understandable without having an in-depth understanding of Hspec and Haskell. 
This provides the option to show some of the tests to the users to give them a more specific idea of what is expected from the exercise. 
Furthermore, Hspec also allows for parallel test execution which is preferable when trying to optimize for larger numbers of users.

An example setup of a Hspec test can be seen below in figure \ref{lst:HspecTestExample}. First, the test frame Hspec and the module defined in the student’s code are imported. Then the specification describing the test Hspec should run in the code is defined. In the figure, the function is called on the variable x and the expected output is y.

\begin{lstlisting}[language=CSharp, caption={An example of a Hspec Test.}, label={lst:HspecTestExample}]
{
 module moduleNameSpec (spec, main) where

 import Test.Hspec
 import moduleName (functionName)
 
 spec = Spec
 spec = do
 	describe "Function Name" do
 	it "Test description" $ do
	functionname x `shouldBe' y
}
\end{lstlisting}

\section*{Rust}
Rust is a multi-paradigm, general-purpose programming language originally developed by Graydon Hoare in 2006 as a personal project at Mozilla. 
The project was then sponsored by Mozilla from 2009 to 2021 where the project along with all trademarks was moved to the newly create Rust Foundation. 
The idea behind Rust was to challenge the idea that high-level ergonomics and low-level control come at the cost of each other\cite{Rust_Book}.
Most other programming languages today operate in a band where either safety or control is valued highest with the other diminished. Such as C and its high level of control and lack of safety. 
Here Rust provides the low-level power of C along with the solid safety features programmers have gotten used to in high-level languages like Python. 
As such, the main overall goal of Rust is to provide as much safety as possible in a low-level programming language without sacrificing any speed\cite{Rust_in_Action}.

In order to achieve this goal Rust provides a large number of safety features among these is its most distinguishing feature which prevents invalid data access at compile time. 
Considering a research article by Microsoft Security Research Center stating that invalid data access is behind 70\% of serious security bugs in modern programs this is a large deal\cite{Safe_Systems_Languages}. 
Instead of relying on the developer to deal with it, Rust's compiler guarantees any compiled program is memory-safe.

Our reason for using Rust is twofold: 
\begin{enumerate}
    \item Rust is compiled to native machine code, which ensures that no additional overhead is introduced by the language itself.
    \item Rust features safe implementations of threading and concurrency which is useful for web applications where scalibility is a priority.
\end{enumerate}

\section*{Docker}
The main purpose of Docker is to simplify deliveries in distributed systems with the use of so-called containers\cite{Docker_Container}.
Containers are bundles of code and required dependencies. This allows developers to move around prepackaged applications ensuring that the developed software runs the same regardless of what system is used\cite{Docker_Container}.
The containers themselves are created from an image. Here the image is the executable package that encapsulates everything required in order to run the application. On runtime, the image is then turned into our container. 
This is possible due to the Linux kernel's build process isolation and virtualization capabilities. These also allow a single host system to share its resources with multiple application components\cite{Docker_Container}.

We use Docker to set up local development environments for the APIs and Databases. This allows for an easier development process and a simplified delivering process to production.

\section*{tRPC}
tRPC is a library that enables developers to build type safe APIs without having to deal with schemas or code generation. 
It is structured in a way that allows for types to be shared between the client and server by only importing the types instead of the actual server code. 
This in turn allows developers to not have the actual server code exposed in the \frontend{}. 
Furthermore, tRPC is created in a way to fully take advantage of the power of a full-stack TypeScript project, which a language-agnostic framework\cite{tRPC}.
In tRPC, a query is like a read operation, while a mutation is similar to create, update, or delete operations.

\section*{Prisma}
Prisma is a 2nd generation object-relational mapper(ORM) developed for usage in Node.js and \typescript{} back-ends. 
The main goal is to increase developers' productivity by allowing them to develop using a type-safe API for database queries that return \javascript{} objects. 
This goal is achieved by providing type-safe database queries allowing for validation at compile time as well as constraints preventing common pitfalls\cite{Prisma_Why}.

The goal for the 2nd generation ORMs is to move closer to raw SQL in terms of high control while improving on the 1st generation ORMs productivity improvements. 
Prisma enables this productivity improvement by allowing developers to define their applications models through a data modeling language allowing an easier way of configuring their applications' data sources and models\cite{Prisma_Doc}.

\section*{TypeScript}
As the server-side use of \javascript{} keeps growing in popularity its inability to provide developers with access to strong type checking and compile time error checking continues to prevent it from being the go-to language.
As a way to address these problems, \typescript{} was designed to try and bridge this gap without requiring developers to learn a new language.
Instead, \typescript{} was developed as a syntactic superset to \javascript{} allowing developers to keep building into their already existing knowledge but with the addition of additional features. 
This also allows for all \javascript{} projects to be converted to \typescript{} projects allowing for easier movement between the two languages\cite{TypeScript}. 
\typescript{} accomplishes this while still keeping the advantages of an interpreted language by compiling all the written instructions to its \javascript{} equivalents during the compilation process. 
This is possible because \typescript{} itself is compiled into \javascript{}, which is an interpreted language. 

\section*{Next.js}
Next.js (Next) is an open-source React framework created by Vercel that enables react web applications to use server-side rendering as well as generate static websites. The Next framework was created in order to counter the potential drawbacks of React relying on client-side rendering such as potential security issues. By enabling websites to be fully or partially server-side rendered instead Next provides a solution to this issues\cite {Nextjs_Docks}. 

Next as a framework also tries to fix another issue of React, namely that creating a website from the ground up still requires a lot of effort spending time configuring tools as well as rebuilding solutions. 
Next tries to combat this by providing the developers with the building blocks needed to build a website.
This is done by handling the tooling and configuration needed while providing additional structure and optimization on top\cite{Nextjs_Docks}.


\section*{PostgreSQL}
PostgreSQL (Postgres) is an open-source object-relational database management system that was originally developed at the University of California, Berkley with the goal of supporting multiple data types with the fewest features needed. Originally only designed for UNIX-like platforms Postgres today runs on all major operating systems like Windows and MacOS\cite{Postgres_Docs}.
As a rule, the Postgres development team tries to conform to the SQL Standards whenever these standards do not contradict Postgres features or when the standards could lead to a deterioration of the architecture or performance\cite{Postgres_Docs}. 

Today Postgres features transactions with supports Atomicity, Consistency, Isolation, and Durability (ACID) properties, as well as automatic update of views, foreign keys, and procedures. 
Furthermore modern Postgres supports a wide variety of deployment options from single machine usage to data warehouses and web services\cite{Postgres_Docs}.




